\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-12 paper.tex
Modify related work
* Replace blockchain with DLT
* Mention why DLT is a solution
* Add MAM feature

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.

@@

By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit and access an encrypted data stream over the Tangle where privacy and integrity meet.

>>>>

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and distributed ledger technology (DLT) is considered a solution, which has the immutable data storage feature that the existence of data can be trusted and no longer rely on any third party authority.

@@

By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit, access and verify an encrypted data stream over the Tangle where privacy and integrity meet.
